\documentclass[review]{elsarticle}
\usepackage{epstopdf}
\usepackage{amssymb} %maths
\usepackage{amsmath} %maths
\usepackage{timet,xcolor,graphicx}

\date{March 2022}

\input{mathdef}
\begin{document}

\title{Kinetic energy transfer during polarity reversal in numerical dynamo simulation}

\author[Tohoku]{Takumi Kera}
\ead{takumi.kera.r1@dc.tohoku.ac.jp}
\author[ucd]{Hiroaki Matsui\corref{cor1}}
\ead{hrmatsui@ucdavis.edu}
\author[TITECH]{Masaki Matsushima}
\ead{masaki.matsushima@eps.sci.titech.ac.jp}
\author[Tohoku]{Yuto Katoh}
\ead{yuto.katoh@tohoku.ac.jp}

\cortext[cor1]{Corresponding author}
\address[Tohoku]{Department of Geophysics, Tohoku University, Sendai, Japan.}
\address[ucd]{Department of the Earth and Planetary Sciences, University of California, Davis, CA, USA.}
\address[TITECH]{Department of Earth and Planetary Sciences, Tokyo Institute of Technology, Tokyo, Japan.}

\begin{keyword}
Geodynamo, Polarity reversals, Equatorial symmetry, Energy transfer
\end{keyword}

\begin{abstract}
The Earth has a magnetic field with a dominant dipole moment nearly parallel to the axis of Earth’s rotation. 
{\color{teal}
It is widely accepted that the geomagnetic field is sustained by fluid motion in the Earth’s outer core, the so-called dynamo action.
}
Paleomagnetic measurements have shown that the geomagnetic field has reversed its polarity many times. 
% It is widely accepted that the geomagnetic field is sustained by fluid motion in the Earth’s outer core, the so-called dynamo action. 
Some geodynamo simulations have been carried out to investigate the physical process of polarity reversals, and the equatorially antisymmetric flow during polarity reversals is found to be stronger than that during stable periods. 
On the other hand, convective motions in a rotating spherical shell have characteristics that the equatorially symmetric flow is dominant due to the effect of rotation. 
{\color{teal}
To investigate energy transfers between the equatorially symmetric and antisymmetric flows, we have performed geodynamo simulations with polarity reversals.
}
% We have performed a geodynamo simulation with polarity reversals, and analyzed energy transfers between the equatorially symmetric and antisymmetric flows.
The energy transfer to the equatorially antisymmetric flow is generally small.
{\color{teal}
Toward a polarity reversal, however, it increases in the following manner;
}
%The energy transfer to the equatorially antisymmetric flow is generally small, but it increases toward a polarity reversal as follows, 
(i) the rate of energy transfer from the equatorially symmetric flow to the magnetic field decreases, (ii) the rate of energy transfer from the equatorially symmetric flow to the antisymmetric flow by the advection increases, and (iii) the energy injection by the buoyancy force into the equatorially antisymmetric flow increases.
The present results suggest that the intense zonal flow caused by the intense upward flow inside the tangent cylinder in the either hemisphere can trigger a polarity reversal of the magnetic field.
\end{abstract}

\maketitle


\input{introduction}
\input{method}


\input{results}

\input{discussion}

\input{conclusions}

\input{reference_mm.tex}
%\input{reference}

\end{document}
